Type Refinements for the Working Class

### 2015-11-12 paper.tex
Activate kerning and spacing for microtype
Set up blackboard bold for digits
Express colimit as Lan
Rearrange the LF to support symbol renaming using fibration
@freebroccolo; does it look like this will work? If so, do you think
there is any nicer way to do it?

\usepackage{pxfonts}
\usepackage{eulervm}

@@

% fonts
\usepackage[
  activate={true,nocompatibility},
  tracking=true
]{microtype}

@@

For any abt signature $\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$ and small worlds
category $\mathcal{W}$, we may deploy a generic logical framework in which the
meaning of a judgment is an object in the presheaf category
$\Define{\mathbb{J}}{\Sets^\mathcal{W}}$ (that is, a judgment is identified
with the intensional set of its derivations).

\begin{definition}[General Judgment]
  For a metavariable context $\IsMetaCtx{\Omega}$, we can define the set
  of its substitutions as the following product:
  \[
    \Define{\square\Omega}{
      \prod_{(\MV{m}:v)\in\Omega} \MkSet{E\mid\IsAbtUnmoded{\cdot}{\cdot}{\cdot}{E}{v}}
    }
  \]
  Let $\Discrete{\square\Omega}$ be the discrete category on $\square\Omega$. Then, for
  any diagram $\Of{\mathcal{J}}{\mathbb{J}^{\Discrete{\square\Omega}}}$, we can
  define the general judgment $\GenJ{\Omega}{\mathcal{J}}$ as follows:
  \[
    \textstyle
    \Define{
      \left(\GenJ{\Omega}{\mathcal{J}}\right)(w)
    }{
      \Hom{\mathbb{J}}{
        \Yoneda{w}
      }{
        \varinjlim_{\Discrete{\square\Omega}}\mathcal{J}
      }
    }
  \]

  Intuitively, the general judgment $\GenJ{\Omega}{\mathcal{J}}$ is evident
  when the family of judgments $\mathcal{J}$ shall forevermore have a section
  (i.e.\ for any substitution $\Member{\omega}{\square\Omega}$,
  $\mathcal{J}(\omega)$ shall be evident). Recall that metavariables have
  \emph{valences} rather than sorts; as such, the general judgment allows us to
  quantify over terms of higher type.  However, for clarity we will often write
  $\GenJ{\MV{m}:\sigma}{\mathcal{J}}$ rather than
  $\GenJ{\MV{m}:\MkValence{\cdot}{\cdot}{\sigma}}{\mathcal{J}}$; likewise, in
  the body of $\mathcal{J}$ we will simply write $\MV{m}$ rather than the more
  proper $\MApp{\MV{m}}{\cdot}{\cdot}$.

>>>>

@@

%% fonts
\usepackage{pxfonts}
\usepackage{eulervm}
\usepackage[
  activate={true,nocompatibility},
  kerning=true,
  spacing=true,
  tracking=true
]{microtype}
\DeclareSymbolFont{bbold}{U}{bbold}{m}{n}
\DeclareSymbolFontAlphabet{\mathbbold}{bbold}

@@

Then, for any abt signature $\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$, we can
deploy a generic logical framework. Recall from \cite{sterling-morrison:2015}
that $\SCtx$ is the category of symbol-contexts and their injective,
sort-preserving renamings. Then, fix a small category $\mathcal{W}$ of worlds
along with a map $\Of{\pi_\mathcal{W}}{\mathcal{W}\to\SCtx}$ such that
$\pi_\mathcal{W}$ is a Grothendieck opfibration. Then, a \emph{judgment} shall
be interpreted as an object in the presheaf category
$\Define{\mathbb{J}}{\Sets^\mathcal{W}}$; in other words, a judgment is
identified with the intensional set of its renaming-sensitive derivations.

\begin{definition}[General Judgment]
  For a metavariable context $\IsMetaCtx{\Omega}$, we can define the presheaf
  of its substitutions $\Of{\square\Omega}{\Sets^\SCtx}$ as follows:
  \[
    \Define{{\square\Omega}\,(\Upsilon)}{
      \prod_{(\MV{m}:v)\in\Omega}
        \MkSet{E\mid\IsAbtUnmoded{\cdot}{\Upsilon}{\cdot}{E}{v}}
    }
  \]

  For any diagram $\Of{\mathcal{J}}{\mathbb{J}^{\square\Omega(\Upsilon)}}$, we can define
  the general judgment $\GenJ{\Omega}{\mathcal{J}}$ as follows, where
  $\Of{\Yoneda{-}}{\mathcal{W}\to\mathbb{J}}$ is the Yoneda Embedding:
   \[
     \textstyle
     \Define{
       \left(\GenJ{\Omega}{\mathcal{J}}\right)(w)
     }{
       \Hom{\mathbb{J}}{
         \Yoneda{w}
       }{
         Lan_{\mathbbold{1}}{\mathcal{J}}
       }
     }
   \]

   Intuitively, the general judgment $\GenJ{\Omega}{\mathcal{J}}$ is evident
   when the family of judgments $\mathcal{J}$ shall forevermore have a section
   (i.e. for any substitution $\Member{\omega}{\square\Omega(\Upsilon)}$,
   $\mathcal{J}(\omega)$ shall be evident). Recall that metavariables have
   \emph{valences} rather than sorts; as such, the general judgment allows us to
   quantify over terms of higher type.  However, for clarity we will often write
   $\GenJ{\MV{m}:\sigma}{\mathcal{J}}$ rather than
   $\GenJ{\MV{m}:\MkValence{\cdot}{\cdot}{\sigma}}{\mathcal{J}}$; likewise, in
   the body of $\mathcal{J}$ we will simply write $\MV{m}$ rather than the more
   proper $\MApp{\MV{m}}{\cdot}{\cdot}$.
